From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-01 Pi+/paper/ufin.tex

>>>>

\begin{center}
  \begin{tikzpicture}[yscale=.5,xscale=2]
    \draw (0,0) arc (-90:170:8ex) node[anchor=south east] {$A$} arc (170:270:8ex);
    \draw (0,6) arc (-90:170:10ex) node[anchor=south east] {$\dsum{x:A}{P(x)}$} arc (170:270:10ex);
    \draw[->] (0,5.8) -- node[auto] {$\fst$} (0,3.2);
    \node[circle,fill,inner sep=1pt,label=left:{$x$}] (b1) at (-.5,1.4) {};
    \node[circle,fill,inner sep=1pt,label=right:{$y$}] (b2) at (.5,1.4) {};
    \draw[decorate,decoration={snake,amplitude=1}] (b1) -- node[auto,swap] {$p$} (b2);
    \node[circle,fill,inner sep=1pt,label=left:{$\pair{x,u}$}] (b1) at (-.5,7.2) {};
    \node[circle,fill,inner sep=1pt,label=right:{$\pair{y,\tr{p}{u}}$}] (b2) at (.5,7.2) {};
    \draw[decorate,decoration={snake,amplitude=1}] (b1) -- node[auto] {$\term{lift}(u,p)$} (b2);
  \end{tikzpicture}
\end{center}
